---
title: "Final Project"
author: "Mike Slathar"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Library

```{r}
library(tidyverse)
library(plotly)
library(DT)
```



## Data

Compiled data from iphone built-in screen-time application into a data frame

```{r}
data=data.frame(Day = c("4/06", "4/07", "4/08", "4/09", "4/10", "4/11", "4/12", "4/13", "4/14", "4/15", "4/16", "4/17", "4/18", "4/19"), Screen_Time=c(3.05, 1.97, 1.55, 2.17, 1.10, 1.02, 4.13, 2.35, 4.07, 2.83, 1.07, 3.8, 2.08, 1.10))

mean(data$Screen_Time)

data
```

## Graphical Visualization

```{r}
myplotbar=data%>%ggplot(aes(x=Day, y=Screen_Time))+
  geom_col(fill="blue")+
  labs(title = "Relationship between Date and Screen-time", x="Date", y="Screen-time (in hours)")+
  theme(axis.text.x = element_text(angle=45, hjust = 1))

myplotbar
```

```{r}
myplotLine=ggplot(data = data, aes(x=Day, y=Screen_Time, group = 1))+
  geom_line(color="blue", size=1)+
  labs(title = "Relationship between Date and Screen-time", x="Date", y="Screen-time (in hours)")+
  theme(axis.text.x = element_text(angle=45, hjust = 1))

myplotLine
```


```{r}
myplotBox=ggplot(data)+
  geom_boxplot(aes(y=Screen_Time), fill="blue")+
  labs(title = "Five-Number Summary of Screen-time", y="Screen-time (in hours)")+
  xlim(-5,5)

myplotBox
```



$\overline{x}:$ my average daily cellular screen-time

$\mu:$ national average daily cellular screen-time

Hypothesis

$H_o: \overline{x} = \mu$ vs $H_a: \overline{x}<\mu$ at $\alpha=0.05$

Testing

```{r}
t.test(data$Screen_Time, mu=4.5, alternative = "less")
```

Conclusion

$p-value<\alpha$. At the $5\%$ significance level, we reject $H_o$, and accept $H_a$. We have sufficient evidence to conclude that my daily average cellular screen-time is significantly lower than the national average daily cellular screen-time or 
$H_a: \overline{x}<\mu$.